Mahotas: Open source software for scriptable computer vision

### 2012-08-21 paper.tex
ENH Add references to other systems

Mahotas is a computer vision library for the Python. It operates on numpy
arrays~\cite{numpy}. Therefore, it uses all the infrastructure built by that
project for storing information. However, its inner loops are implemented in
\cpp{} for speed and ease of implementation.

@@

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features.
\item[Wavelet] Haar and Daubechies wavelets.
\item[features] Some feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations.
\item[watershed] seeded watershed.
\item[polygon operations] convex hull, polygon drawing.
\end{description}

@@

Mahotas does not include machine learning related functionality, such as
$k$-means clustering or any classification. This is the result of an explicit
design decision. Specialised machine learning packages for Python (e.g.,
milk\footnote{http://github.com/luispedro/milk},
scikit-learn\footnote{http://}) already exist. A good classification system can
benefit both computer vision users and others. As these projects all use Numpy
arrays as their datatypes, it is easy to use functionality from the different
project seamlessly (including without any extra copying of data).

>>>>

Mahotas is a computer vision library for the Python. It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information.

Python is a natural ``glue'' language: it is easy to use state-of-the-art
libraries written in multiple languages~\citep{10.1109/MCSE.2007.58}. Mahotas
itself is a mix of high-level Python and low-level \cpp{}. This achieves a good
balance between speed and ease of implementation.

@@

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}.
\item[Wavelet] Haar and Daubechies wavelets.
\item[features] Some feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations.
\item[watershed] seeded watershed.
\item[polygon operations] convex hull, polygon drawing.
\end{description}

@@

Mahotas does not include machine learning related functionality, such as
$k$-means clustering or any classification. This is the result of an explicit
design decision. Specialised machine learning packages for Python (e.g.,
milk\footnote{http://github.com/luispedro/milk},
scikit-learn\footnote{http://scikit-learn}) already
exist~\citep{Pedregosa:2011:SML:2078183.2078195}. A good classification (or
other) system can benefit both computer vision users and others. As these
projects all use Numpy arrays as their data types, it is easy to use
functionality from the different project seamlessly (no copying of data is
necessary).
